Reading Notes

### 2020-08-11 2pd.tex

It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.

@@

<gain insight into the limits of coarse graining>
<create models for new opv compounds>
<create a workflow that will make creating new models more accessible>
<develop new tools that help humans do science>
<use that science to help solve energy crisis???????>
<I don't know where to put this but I want a section on best practices>
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}

>>>>

It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies. %EJ: NIIICE SENTENCE.

@@

<gain insight into the limits of coarse graining>
%EJ: Nice. Attempting to reorder based on heirarchy
<use that science to help solve energy crisis???????>
<create models for new opv compounds>
<gain insight into the limits of coarse graining>
<develop new tools that help humans do science>
<create a workflow that will make creating new models more accessible>
<I don't know where to put this but I want a section on best practices>
%EJ: Learning and incorporating best practices might actually be a new facet of your work. Like, we can point to the computational research papers that show how this wasn't done so much in the past, but it's happening better now, and we're going to lean into it- I think it fits.
By making our code open source and freely availiable, we contribute to the knowledge of a global community. But just because something is availiable doesn't mean it is accessible. 
lazy refactoring--get something working first then update it when needed, keep code small and modular to make this easier and more understandable\cite{Adorf2018a} 
Best practices for jupyter notebooks -- like a lab notebook-- can show the process and the story of each assignment and the exact steps and results to get there\cite{Rule2019a}
Using software carpentry principles to keep in mind how people learn when introducing a new concept\cite{https://v4.software-carpentry.org/softeng/principles.html}
Software carpentry using version control, building, scripting, testing, debugging,\cite{Wilson2006}
live coding, interactive \cite{Wilson2016}
reducing cognitive load \cite{Jankowski2019}
using the tools, not fighting them--version control, automation \cite{Wilson2014}
TRUE\cite{Thompson2020}
